% User Manual

\chapter{User Manual}

\section{Introduction}
Welcome to the Nexora User Manual. This guide is designed to help you understand and use the Nexora e-commerce platform effectively. Whether you are a customer, vendor, or administrator, this manual provides step-by-step instructions and helpful tips for all major features.

\section{Getting Started}
\subsection{Accessing Nexora}
Nexora is a web-based application accessible from any modern browser. Visit the official Nexora website to begin.

\subsection{Creating an Account}
\begin{enumerate}
    \item Click on the \textbf{Register} button on the homepage.
    \item Fill in your details (name, email, password, and role: Customer or Vendor).
    \item Agree to the terms and conditions and submit the form.
    \item You will receive a confirmation email. Click the link to activate your account.
\end{enumerate}

\subsection{Logging In}
\begin{enumerate}
    \item Click on the \textbf{Login} button.
    \item Enter your registered email and password.
    \item Click \textbf{Login} to access your dashboard.
\end{enumerate}

\subsection{Navigating the Dashboard}
After logging in, you will see a dashboard tailored to your role (Customer, Vendor, or Admin). Use the navigation menu to access different features.

\section{Features and Functionality}
\subsection{For Customers}
\begin{itemize}
    \item \textbf{Browse Products:} View and search for products by category, name, or vendor.
    \item \textbf{Product Details:} Click on a product to see detailed information, images, reviews, and available variants.
    \item \textbf{Shopping Cart:} Add products to your cart and view your selections at any time.
    \item \textbf{Checkout:} Complete your purchase by providing shipping details and payment information.
    \item \textbf{Order Tracking:} Track the status of your orders in real time from your dashboard.
    \item \textbf{Wishlist:} Save products to your wishlist for future reference.
    \item \textbf{Product Reviews:} Leave reviews and ratings for products you have purchased.
\end{itemize}

\subsection{For Vendors}
\begin{itemize}
    \item \textbf{Product Management:} Add, edit, or remove products from your catalog.
    \item \textbf{Order Processing:} View and manage incoming orders, update order status, and communicate with customers.
    \item \textbf{Sales Analytics:} Access sales reports and analytics to monitor your business performance.
    \item \textbf{Inventory Management:} Track stock levels and update inventory as needed.
    \item \textbf{Profile Settings:} Update your business profile and contact information.
\end{itemize}

\subsection{For Administrators}
\begin{itemize}
    \item \textbf{User Management:} View, approve, or deactivate user accounts (customers and vendors).
    \item \textbf{Product Oversight:} Monitor all products listed on the platform and manage categories.
    \item \textbf{Order Management:} Oversee all orders, resolve disputes, and ensure smooth operations.
    \item \textbf{System Configuration:} Manage platform settings, featured products, and promotional banners.
    \item \textbf{Analytics and Reporting:} Access comprehensive reports on platform activity and performance.
\end{itemize}

\section{FAQ}
\begin{description}
    \item[Q: I forgot my password. What should I do?]
    A: Click on the \textbf{Forgot Password} link on the login page and follow the instructions to reset your password.

    \item[Q: How do I contact customer support?]
    A: Use the \textbf{Contact Us} form available in the website footer or email support@nexora.com.

    \item[Q: Can I change my account role after registration?]
    A: For security reasons, changing roles requires admin approval. Please contact support for assistance.

    \item[Q: How do I track my order?]
    A: Go to your dashboard, select \textbf{Orders}, and view the status of each order.

    \item[Q: How do I become a vendor?]
    A: Register as a vendor during sign-up or request a role change through your profile settings.

    \item[Q: What payment methods are supported?]
    A: Nexora supports major credit/debit cards and online payment gateways. Details are provided at checkout.
\end{description} 